---
title: "Usage statistics"
subtitle: "MBO rekenen pilot 2024"
author: "Maarten van der Velde"
date: "Last updated: `r Sys.Date()`"
output:
  html_notebook:
    smart: no
    toc: yes
    toc_float: yes
  github_document:
    toc: yes
editor_options: 
  chunk_output_type: inline
---

```{r}
library(here)
library(data.table)
library(ggplot2)
library(jsonlite)
library(purrr)

theme_memorylab_url <- "https://raw.githubusercontent.com/SlimStampen/theme_memorylab/master/theme_memorylab.R"
source(theme_memorylab_url)

source(here("..", "databases", "database_functions.R"))
```

# Noorderpoort

```{r}
np_domain <- query_db("SELECT * FROM domain WHERE name = 'noorderpoort.memorylab.app';", database = "slimstampen")
```

Users registered on this domain:
```{r}
np_users <- query_db(paste0("SELECT id AS user_id, email FROM users WHERE domain_id = ", np_domain$id, ";"), database = "slimstampen")
```

Lessons on this domain:
```{r}
np_lessons <- query_db(paste0("SELECT * FROM lesson WHERE domain_id = ", np_domain$id, ";"), database = "slimstampen")
```

Sessions from users on this domain during the pilot period:
```{r}
np_sessions <- query_db(paste0("SELECT * FROM session WHERE token_id = 2 AND user_id IN (", paste(np_users$user_id, collapse = ", "), ");"), database = "ssaas")
np_sessions <- np_sessions[create_time > "2024-10-06"][create_time < "2024-11-05"]
```

When were these sessions?
```{r}
np_sessions[, session_date := as.Date(create_time)]

np_test_dates <- data.table(test = c("Toets 1", "Toets 2"),
                            date = as.Date(c("2024-10-07", "2024-11-04")))

ggplot(np_sessions, aes(x = session_date)) +
  geom_vline(data = np_test_dates, aes(xintercept = date), linetype = "dashed", colour = "grey50") +
  geom_label(data = np_test_dates, aes(x = date, y = Inf, label = test), vjust = 1.05, hjust = .5, colour = "grey50") +
  geom_histogram(binwidth = 1, fill = colours_memorylab[1]) +
  labs(x = "Datum", y = "MemoryLab oefensessies per dag", title = "MemoryLab oefenactiviteit over de tijd") +
  scale_x_date(date_labels = "%d/%m", date_breaks = "1 week", limits = c(as.Date("2024-10-06"), as.Date("2024-11-05"))) +
  scale_y_continuous(expand = c(0, 0)) +
  theme_ml() +
  theme(panel.grid.major.y = element_line(colour = "grey90"))

ggsave(here("output", "memorylab_oefensessies_over_tijd.png"), width = 10, height = 5)
```

```{r}
```

Most popular days:
```{r}
np_sessions[, .N, by = .(session_date)][order(-N)]
```
Total sessions:
```{r}
nrow(np_sessions)
```

Sessions per user:
```{r}
np_sessions[, .N, by = user_id][order(-N)]
```

Total users with at least one session:
```{r}
length(unique(np_sessions$user_id))
```


Which lessons did users do? Parse the session context:
```{r}
np_sessions[, context_parsed := map(context, function (x) {
  x <- fromJSON(x)
  data.table(lesson_id = x$lessonId,
             lesson_group_id = x$lessonGroupId,
             title = x$title)
})]

np_sessions_parsed <- np_sessions[, rbindlist(context_parsed), by = .(session_id = id, user_id, create_time, session_date)]
```

Practice by lesson:
```{r}
np_sessions_parsed[, .(`Keer geoefend` = .N), by = .(Les = title)][order(-`Keer geoefend`)] |> knitr::kable()
```

We can link each practice session to one of the test topics:
```{r}
np_lesson_groups <- data.table(
  lesson_group_id = c(
    29092,
    29087,
    29096,
    29089,
    29098,
    29086,
    29097,
    29095,
    29090,
    29088,
    29094,
    29091),
  topic = c(
    "Rekentaal",
    "Breuken",
    "Percentage",
    "Eenheden",
    "Delen",
    "Afronden",
    "Cijfers",
    "Vermenigvuldigen",
    "Aftrekken & Optellen",
    "Decimalen",
    "Tafels",
    "Rekentaal"
  )
)

# Set lesson topics to the right order
np_lesson_groups[, topic := factor(topic, levels = c("Delen",
                                                     "Percentage",
                                                     "Cijfers",
                                                     "Breuken",
                                                     "Tafels",
                                                     "Decimalen",
                                                     "Aftrekken & Optellen",
                                                     "Vermenigvuldigen",
                                                     "Afronden",
                                                     "Eenheden",
                                                     "Rekentaal"))]


np_lessons <- merge(np_lessons, np_lesson_groups, by = "lesson_group_id")
np_sessions_parsed <- merge(np_sessions_parsed, np_lesson_groups, by = "lesson_group_id")
```

Practice by lesson topic:
```{r}
np_sessions_parsed[, .(`Keer geoefend` = .N), by = .(Onderwerp = topic)][order(-`Keer geoefend`)] |> knitr::kable()
```

Bar plot of sessions per topic:
```{r}
np_sessions_parsed[, .(`Keer geoefend` = .N), by = .(Onderwerp = topic)] |>
  ggplot(aes(x = Onderwerp, y = `Keer geoefend`)) +
  geom_col(fill = colours_memorylab[1]) +
  labs(x = "Onderwerp", y = "Keer geoefend", caption = "Data from noorderpoort.memorylab.app") +
  theme_ml()
```


Mastery credits:
```{r}
np_credits <- query_db(paste0("SELECT * FROM lesson_mastered WHERE user_id IN (", paste(np_users$user_id, collapse = ", "), ");"), database = "slimstampen")

# Add lesson titles and topics
np_credits <- merge(np_credits, np_lessons[, .(lesson_id = id, title, topic)])
```

Credits by topic:
```{r}
np_credits[, .N, by = .(topic)][order(-N)]
```

Responses from these user_ids:
```{r}
np_responses <- query_db(paste0("SELECT * FROM response WHERE token_id = 2 AND user_id IN (", paste(np_users$user_id, collapse = ", "), ");"), database = "ssaas")
np_responses <- np_responses[create_time > "2024-10-06"][create_time < "2024-11-05"]

# Add lesson titles and topics
np_responses <- merge(np_responses, np_sessions_parsed[, .(session_id, title, topic)], by = "session_id")
```

Responses by user:
```{r}
np_responses[, .N, by = .(user_id)][order(-N)]
```

Responses by topic:
```{r}
np_responses[, .N, by = .(topic)][order(-N)]
```





```{r}
ggplot(np_responses, aes(x = as.Date(create_time))) +
  geom_histogram(binwidth = 1, fill = colours_memorylab[1]) +
  labs(x = "Date", y = "Responses per day", caption = "Data from noorderpoort.memorylab.app") +
  scale_y_continuous(expand = c(0, 0), labels = scales::number_format(big.mark = ",")) +
  theme_ml() +
  theme(panel.grid.major.y = element_line(colour = "grey90"))
```
 
Split by lesson topic:
```{r}
ggplot(np_responses, aes(x = as.Date(create_time))) +
  geom_histogram(aes(fill = topic), binwidth = 1) +
  labs(x = "Date", y = "Responses per day", fill = "Onderwerp", caption = "Data from noorderpoort.memorylab.app") +
  scale_y_continuous(expand = c(0, 0), labels = scales::number_format(big.mark = ",")) +
  scale_fill_viridis_d() +
  theme_ml() +
  theme(panel.grid.major.y = element_line(colour = "grey90"))

```
 

## How does study behaviour on specific topics relate to test performance?

We want to see whether studying a specific topic is related to an increase in test performance.
Studying behaviour can be summarised in several ways: time spent, number of sessions, number of questions answered, number of credits achieved.

```{r}
np_session_stats <- np_responses[, .(
  n_responses = .N,
  duration = max(presentation_start_time) + presentation_duration[which.max(presentation_start_time)] - min(presentation_start_time),
  accuracy = mean(correct)
), by = .(user_id, topic, session_id)]

np_practice_stats <- np_session_stats[, .(
  n_sessions = .N,
  n_responses = sum(n_responses),
  duration = sum(duration),
  accuracy = mean(accuracy)
), by = .(user_id, topic)]
```

Load test scores per topic:
```{r}
np_test_scores <- fread(here("data", "test", "noorderpoort_scores_by_topic.csv"))
np_test_scores[, Email := tolower(trimws(Email))]

# Link to MemoryLab user IDs
np_test_scores <- merge(np_test_scores, np_users, by.x = "Email", by.y = "email", all = TRUE)
```

There are some test scores for which we don't have any associated MemoryLab data:
```{r}
np_test_scores[is.na(user_id), .(unique(Email))]
```

There are also some MemoryLab users for which we don't have any associated test scores:
```{r}
np_test_scores[is.na(component), .(unique(Email))]
```

For this analysis we'll only include users of whom we have two test scores as well as some MemoryLab practice data.
```{r}
np_test_scores[, did_ml := !is.na(user_id)]
np_test_scores[, two_tests := uniqueN(test) == 2, by = .(user_id)]
np_test_scores[, include_user := did_ml & two_tests]
```

Mean test scores from included students:
```{r}
np_test_scores[include_user == TRUE & component == "Totaal punten", .(mean_grade = 10*mean(score)/40), by = test]
```

Distribution of test scores:
```{r}
np_test_scores[include_user == TRUE & component == "Totaal punten", .(test, score)] |>
  ggplot(aes(x = 10*score/40, fill = test)) +
  geom_density(alpha = 0.5) +
  labs(x = "Score", y = "Density", fill = "Test", caption = "Data from noorderpoort.memorylab.app") +
  scale_x_continuous(breaks = seq(0, 10, 1), limits = c(0, 10)) +
  theme_ml()
```

Do a paired t-test to show that the difference is significant:
```{r}
test_score_dat <- np_test_scores[include_user == TRUE & component == "Totaal punten", .(user_id, test, score)] |>
  dcast(user_id ~ test, value.var = "score")

test_score_dat

t.test(test_score_dat$Posttest, test_score_dat$Pretest, paired = TRUE)
```



Combine data:
```{r}
np_scores <- np_test_scores[include_user == TRUE & !component %in% c("Totaal punten", "Cijfer"), .(
  user_id,
  topic = component,
  score,
  test
)]
np_scores <- dcast(np_scores, user_id + topic ~ test, value.var = "score")
setnames(np_scores, c("Posttest", "Pretest"), c("score_test_2", "score_test_1"))
np_scores[, score_test_change := score_test_2 - score_test_1]
# np_scores[, topic := factor(topic, levels = c("Delen",
#                                               "Percentage",
#                                               "Cijfers",
#                                               "Breuken",
#                                               "Tafels",
#                                               "Decimalen",
#                                               "Aftrekken & Optellen",
#                                               "Vermenigvuldigen",
#                                               "Afronden",
#                                               "Eenheden",
#                                               "Rekentaal"))]

np_scores_and_practice <-  merge(np_scores, np_practice_stats, by = c("user_id", "topic"), all.x = TRUE)

# If a user has no practice data, we'll fill in zeros
np_scores_and_practice[is.na(n_sessions), n_sessions := 0]
np_scores_and_practice[is.na(n_responses), n_responses := 0]
np_scores_and_practice[is.na(duration), duration := 0]
```


Plot of scores:
```{r}
mean_scores <- np_scores_and_practice[, .(score_test_1 = mean(score_test_1), score_test_2 = mean(score_test_2)), by = .(topic)] |>
  melt(id.vars = "topic", variable.name = "test", value.name = "score")

p_scores <- melt(np_scores_and_practice, measure.vars = c("score_test_1", "score_test_2"), variable.name = "test", value.name = "score") |>
  ggplot(aes(x = test, y = score)) +
  facet_wrap(~ topic, ncol = 5) +
  geom_point(alpha = .4, size = .5) +
  geom_line(aes(group = user_id), alpha = .4, lty = 3) +
  geom_point(data = mean_scores, colour = colours_memorylab[1], size = 2.5) +
  geom_line(data = mean_scores, aes(group = topic), colour = colours_memorylab[1], lwd = 1) +
  scale_x_discrete(labels = c("1", "2")) +
  labs(x = "Toetsmoment", y = "Score", title = "Toetsscores") +
  theme_ml() +
  theme(panel.grid.major.y = element_line(colour = "grey90"),
        strip.text = element_text(face = "bold")
        )

p_scores

ggsave(here("output", "testscores_noorderpoort.png"), width = 8, height = 5)

```

How much was each topic practiced?
```{r}
ggplot(np_scores_and_practice, aes(x = n_responses)) +
  facet_wrap(~ topic, ncol = 5) +
  geom_histogram(binwidth = 20, fill = colours_memorylab[1]) +
  labs(x = "Number of practice responses per student", y = "Frequency", colour = "Topic", caption = "Data from noorderpoort.memorylab.app") +
  theme_ml()
```

Did students choose to practice topics on which their pretest score was low?
```{r}
# Add mean pretest scores per topic
mean_pretest_scores <- mean_scores[test == "score_test_1", .(topic, mean_score = round(score, 2))]
np_scores_and_practice <- merge(np_scores_and_practice, mean_pretest_scores, by = "topic")
np_scores_and_practice[, topic_label := paste0(topic, "\n(Gemiddelde score: ", mean_score, ")")]

ggplot(np_scores_and_practice, aes(x = score_test_1, y = n_responses)) +
  facet_wrap(~ topic_label, ncol = 5) +
  geom_point(aes(fill = as.factor(score_test_1)), colour = "black", alpha = .8, position = position_jitter(height = 0, width = .1, seed = 0), pch = 21) +
  scale_fill_brewer(palette = "RdYlGn") +
  guides(fill = "none") +
  labs(x = "Score op Toets 1", y = "Aantal gemaakte MemoryLab oefeningen", colour = "Onderwerp", caption = "noorderpoort.memorylab.app") +
  theme_ml() +
  theme(panel.grid.major.x = element_line(colour = "grey90"),
        panel.grid.major.y = element_line(colour = "grey90"),
        strip.text = element_text(face = "bold"))
```

Interpretation: not really.


Same plot but with totals instead of individual values:
```{r}
p_practice <- np_scores_and_practice[, .(n_sessions_total = sum(n_sessions)), by = .(topic_label, score_test_1)] |>
  ggplot(aes(x = score_test_1, y = n_sessions_total)) +
  facet_wrap(~ topic_label, ncol = 5) +
  geom_col(aes(fill = as.factor(score_test_1)), colour = "black", alpha = .8) +
  scale_fill_brewer(palette = "RdYlGn") +
  guides(fill = "none") +
  labs(x = "Score op Toets 1", y = "Aantal MemoryLab oefensessies", colour = "Onderwerp", title = "Oefenactiviteit") +
  theme_ml() +
  theme(panel.grid.major.x = element_line(colour = "grey90"),
        panel.grid.major.y = element_line(colour = "grey90"),
        strip.text = element_text(face = "bold"))

p_practice

ggsave(here("output", "memorylab_oefensessies_noorderpoort.png"), width = 9, height = 5)
```


Combined plot:
```{r}
library(patchwork)

p_scores + p_practice + plot_layout(ncol = 1)
ggsave(here("output", "memorylab_oefening_en_scores_noorderpoort.png"), width = 10, height = 10)
```



Is there a relation between score change and the number of practice sessions?
```{r}
np_scores_and_practice[, .(n_sessions = sum(n_sessions), score_test_change = mean(score_test_change)), by = .(topic_label)]

ggplot(np_scores_and_practice, aes(x = n_sessions, y = score_test_change)) +
  facet_wrap(~ topic) +
  geom_smooth(method = "lm", colour = colours_memorylab[1]) +
  geom_point(alpha = .25) +
  labs(x = "Number of practice sessions", y = "Change in test score", colour = "Topic", caption = "Data from noorderpoort.memorylab.app") +
  scale_colour_viridis_d() +
  theme_ml()
```

It looks like there might be a positive effect of practice.
Let's look at it more simply:
Is there a relation between score change and whether or not the student has practiced the topic at all?
```{r}
np_scores_and_practice[, did_practice := n_responses > 0]

avg_score_change <- np_scores_and_practice[, .(mean_score_test_change = mean(score_test_change)), by = .(topic, topic_label, did_practice)]

ggplot(np_scores_and_practice, aes(x = did_practice, y = score_test_change)) +
  facet_wrap(~ topic) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_violin(fill = "midnightblue", width = .25, alpha = .8) +
  geom_point(data = avg_score_change, aes(y = mean_score_test_change), size = 2, fill = "white", pch = 21) +
  geom_label(data = avg_score_change, aes(y = mean_score_test_change, label = round(mean_score_test_change, 2)), nudge_x = .33) +
  scale_x_discrete(labels = c("No", "Yes")) +
  labs(x = "Did the student practice the topic?", y = "Change in test score", colour = "Topic", caption = "Data from noorderpoort.memorylab.app") +
  theme_ml()

```

Average change:
```{r}
np_scores_and_practice[, .(N = .N, mean_score_test_change = mean(score_test_change), sd_score_test_change = sd(score_test_change)), by = .(topic, topic_label, did_practice)]
```

Is there a significant difference in score change between students who practiced and those who didn't, taking into account differences in score on the first test?
```{r}
library(lmerTest)

lmer(score_test_change ~ did_practice*score_test_1 + (1 | user_id), data = np_scores_and_practice) |>
  summary()
```
Yes: practicing is associated with an increase in score change of .96; scoring a point higher on test 1 is associated with a lower score change (-.30).

```{r}
lmer(score_test_change ~ did_practice*topic + (1 | user_id), data = np_scores_and_practice) |>
  summary()
```




On some topics, performance on the pretest was already really high, in which case we would not expect much improvement from practice.
Let's look at the relation between pretest score and score change, taking into account whether the student practiced or not:
```{r}
ggplot(np_scores_and_practice, aes(x = score_test_1, y = score_test_2, colour = did_practice)) +
  facet_wrap(~ topic, ncol = 5) +
  geom_abline(intercept = 0, slope = 1, linetype = 2) +
  geom_smooth(method = "lm") +
  geom_point(alpha = .25) +
  labs(x = "Pretest score", y = "Posttest score", colour = "Did the student\npractice the topic?", caption = "Data from noorderpoort.memorylab.app") +
  theme_ml() +
  coord_fixed(xlim = c(0, 4), ylim = c(0, 4))
```


Let's look at performance during practice.
Accuracy by topic:
```{r}
ggplot(np_practice_stats, aes(x = as.character(topic), y = accuracy, fill = topic)) +
  geom_boxplot() +
  geom_jitter(width = .1, height = 0, alpha = .5) +
  labs(x = "Topic", y = "Accuracy", fill = "Topic") +
  scale_y_continuous(limits = c(.4, 1), labels = scales::percent) +
  scale_fill_viridis_d() +
  guides(fill = "none") +
  theme_ml() +
  theme(panel.grid.major.y = element_line(colour = "grey"))
```

Accuracy by user:
```{r}
np_practice_stats[n_responses > 10, .(mean_accuracy = mean(accuracy), sd_accuracy = sd(accuracy)), by = .(user_id)]

ggplot(np_practice_stats[n_responses > 10], aes(x = reorder(as.character(user_id), accuracy), y = accuracy)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(aes(colour = as.character(topic)), width = .1, height = 0, alpha = .25) +
  labs(x = "Student", y = "Accuratesse", colour = "Onderwerp") +
  scale_y_continuous(limits = c(.4, 1), labels = scales::percent) +
  scale_colour_viridis_d() +
  guides(fill = "none") +
  theme_ml() +
  theme(panel.grid.major.y = element_line(colour = "grey"),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank())
```

Speed of forgetting by fact and topic:
```{r}
np_fact_ids <- unique(np_responses$fact_id)
np_facts <- query_db(paste0("SELECT id AS fact_id, text FROM fact WHERE id IN (", paste(np_fact_ids, collapse = ", "), ")"), database = "ssaas")
np_facts[, text := gsub("\\+", " ", text)]
np_facts[, text := URLdecode(text)]
np_facts[, text := gsub("\n", " ", text, fixed = TRUE)]
np_facts[, text := gsub("＋", "+", text, fixed = TRUE)]

np_responses <- merge(np_responses, np_facts, by = "fact_id")

np_sof <- np_responses[, .(final_alpha = alpha[which.max(presentation_start_time)]), by = .(text, topic, user_id)]
np_sof_avg <- np_sof[, .(N = .N, sof_mean = mean(final_alpha), sof_se = sd(final_alpha)/sqrt(.N)), by = .(text, topic)]
```

```{r fig.height = 15, fig.width = 8}
ggplot(np_sof_avg[N > 10], aes(x = sof_mean, y = tidytext::reorder_within(text, sof_mean, as.character(topic)), alpha = N)) +
  facet_grid(as.character(topic) ~ ., scales = "free_y") +
  geom_errorbarh(aes(xmin = sof_mean - sof_se, xmax = sof_mean + sof_se), height = 0, colour = colours_memorylab[5]) +
  geom_point(colour = colours_memorylab[5]) +
  labs(y = "Feit", x = "Vergeetsnelheid (hoger = moeilijker)", alpha = "Geoefend door\naantal studenten") +
  theme_ml() +
  scale_x_continuous(limits = c(.1, .5)) +
  tidytext::scale_y_reordered() +
  theme(axis.text.y = element_text(size = 4),
        panel.grid.major.x = element_line(colour = "grey90"))

ggsave(here("output", "sof_by_fact_and_topic.png"), height = 15, width = 8)
```




# Conclusies Noorderpoort

Studenten scoren gemiddeld lager op de posttest dan op de nulmeting.

Er zijn een aantal factoren die een rol spelen:

   - Studenten hebben niet zo veel geoefend.
   - De oefening die wel gebeurde vond over het algemeen vrij ver van de posttest plaats.
   - Het startniveau van deze studenten was al vrij hoog, waardoor er minder ruimte voor verbetering was, en extra oefening in deze vorm wellicht niet zo zinvol was.
   - Als we kijken naar de combinatie van testscores en oefenactiviteit op individuele onderdelen, zien we een aantal patronen:
    - Veel oefening gebeurde op onderdelen waar het startniveau al hoog was, zoals Afronden, Aftrekken & Optellen, 


---


# Alfa college

```{r}
alfa_domain <- query_db("SELECT * FROM domain WHERE name = 'alfa.memorylab.app';", database = "slimstampen")
```

Users registered on this domain:
```{r}
alfa_users <- query_db(paste0("SELECT id AS user_id FROM users WHERE domain_id = ", alfa_domain$id, ";"), database = "slimstampen")
```

Lessons on this domain:
```{r}
alfa_lessons <- query_db(paste0("SELECT * FROM lesson WHERE domain_id = ", alfa_domain$id, ";"), database = "slimstampen")
```

Sessions from users on this domain during the pilot period:
```{r}
alfa_sessions <- query_db(paste0("SELECT * FROM session WHERE token_id = 2 AND user_id IN (", paste(alfa_users$user_id, collapse = ", "), ");"), database = "ssaas")
alfa_sessions <- alfa_sessions[create_time > "2024-11-01"]
```

When were these sessions?
```{r}
alfa_sessions[, session_date := as.Date(create_time)]

ggplot(alfa_sessions, aes(x = session_date)) +
  geom_histogram(binwidth = 1, fill = colours_memorylab[1]) +
  labs(x = "Date", y = "Sessions per day", caption = "Data from alfa.memorylab.app") +
  scale_y_continuous(expand = c(0, 0)) +
  theme_ml() +
  theme(panel.grid.major.y = element_line(colour = "grey90"))
```

Most popular days:
```{r}
alfa_sessions[, .N, by = .(session_date)][order(-N)]
```
Total sessions:
```{r}
nrow(alfa_sessions)
```

Sessions per user:
```{r}
alfa_sessions[, .N, by = user_id][order(-N)]
```

Total users with at least one session:
```{r}
length(unique(alfa_sessions$user_id))
```


Which lessons did users do? Parse the session context:
```{r}
alfa_sessions_parsed <- alfa_sessions[, map_dfr(context, fromJSON)] |> setDT()
```

```{r}
alfa_sessions_parsed[, .(`Keer geoefend` = .N), by = .(Les = title)][order(-`Keer geoefend`)] |> knitr::kable()
```

Mastery credits:
```{r}
alfa_credits <- query_db(paste0("SELECT * FROM lesson_mastered WHERE user_id IN (", paste(alfa_users$user_id, collapse = ", "), ");"), database = "slimstampen")
```

Add lesson titles:
```{r}
alfa_credits <- merge(alfa_credits, alfa_lessons[, .(lesson_id = id, title)])
```

```{r}
alfa_credits[, .N, by = .(title)][order(-N)]
```




```{r}
query_db(query = "SELECT *
FROM pg_catalog.pg_tables
WHERE schemaname != 'pg_catalog' AND 
    schemaname != 'information_schema';",
         database = "slimstampen")
```

